A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-06 results.tex
resolved the one remaining todo

\noindent\textbf{Actionability of adding Option to a type:} When the user's specification requires a variable to be able to assume \texttt{None} values, these patterns indicate the need to modify the program accordingly. A program repair\todo{is this really a repair tool or a refactoring tool? I feel like many of our changes are for refactorings not repairs, despite our PR} tool can leverage these patterns to automatically update the variable's type to \texttt{Option<T>}, ensuring that it can now hold \texttt{None} as a valid value. Furthermore, such a tool should also systematically update other occurrences of that variable throughout the program to account for the change and ensure program correctness.

>>>>

\noindent\textbf{Actionability of adding Option to a type:} When the user's specification requires a variable to be able to assume \texttt{None} values, these patterns indicate the need to modify the program accordingly. A program repair tool can leverage these patterns to automatically update the variable's type to \texttt{Option<T>}, ensuring that it can now hold \texttt{None} as a valid value. This pattern is a part of a \textit{fix-induced} change, thus, a repair tool should also systematically update other occurrences of that variable throughout the program to account for the change and ensure program correctness.
